Formal Analysis of Rate-Monotonic Scheduling Implementation via Real-Time Maude

### 2015-09-10 RMS/submission.tex
add part of Sect. 3.1

>>>>

\subsection{Formulation of the Standard Setting}
The frequently used setting of the RMS algorithm for analysis
considers a task set consisting only of $n$ periodic tasks
$\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
computation time $C_i$. First jobs of all tasks are assumed to be
instantiated simultaneously.  This means that jobs corresponding to
task $\tau_i$ are initiated at times $kT_i, k\ge 0$. The job initiated
at time $kT_i$ has $(k+1)T_i$ as its deadline, the initiation time of
the next job. The RMS algorithm chooses the labeling such that $T_1\le
T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority
$i$. The following assumptions are made:

(A1) Computation time $C_i$ for each task $\tau_i$ is constant and
does not vary with time.

(A2) Tasks are independent, such that they are ready to run at their
initiation times and can be preempted instantly (ignoring all
blocking).

(A3) All overhead, such as task swapping times, is ignored.
